---
title: "Eating Out"
author: "Diana Flores"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Is there a difference based on frequency in ethnicity's in how often they eat out?

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r eval=TRUE, include=F}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```




# Method
The response variable ( how frequently different races go out to eat)is numerical;the input variable is categorical.We have a Num~Cat

# Descriptive Results

# Graphical Results 

```{r}
barchartGC(~race+eatout,data=mydata)
barchartGC(~race+eatout,data=mydata,type="percent")
```


The bar chart suggests that there is a difference in the percentage of white ethnicity to other ethnicity in eating out.

### Numerical Description 



```{r}
table1 <- xtabs(~race+eatout,data=mydata)
rowPerc(table1)
colPerc(table1)

```
In this numerical descriptions states and shows the frequency of eating out in white ethnicity as apposed to black and other.The table shows that white ethnicity  as frequency of eating out is more than black and other ethnicity 

### Inferential results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=TRUE)
```

Chi squared test shows that the P value is 0.0008179, we see the number is small that we reject the null hypothesis.
The fisher XY test for count data shows that the p value 0.001208
is also very small that we reject the null hypothesis.

# Discussion and Conclution 


Base on the results, we reject the null hypothesis because the p-value is so small, 0.0008179 , concluding that the there is a difference in the frequency of eating out among the ethnicity's.

